
%==============================================================================2
%==============================================================================
%==============================================================================
%==============================================================================
\hypertarget{ch5}{\chapter{Conclusions}\label{ch5}}

Mountain snowpacks are likely to continue declining, with greater uncertainty expected as global warming destabilizes hydroclimatic relationships \citep{millyStationarityDeadWhither2008}. In the snowmelt-dominated WUS, the ability to accurately predict snowmelt water resources will be paramount as annual variability is expected to rise. We must continue to grow our understanding of the spatial characteristics of mountain snowpacks to adapt our water management strategies in an uncertain future. The research described in this dissertation will help advance our ability to monitor snowpacks using two distinct approaches: mountain hydroclimatology and radar remote sensing of snow. We had three main findings in this work. First, we showed physiography (i.e., elevation, slope, and aspect) exhibits significant control on midwinter snowmelt in the Sierra Nevada. This midwinter melt propagates into MSWE magnitude and timing, and shows different sensitivities depending on elevation and aspect. Motivated by our work showing the spatial complexities of snowpack processes, we next used L-band InSAR to estimate both snow ablation and accumulation effectively. This finding further shows the robustness of the technique and was a substantial step forward in preparation for NISAR. Lastly, we demonstrated the moderate-resolution NDSI-based optical products are sufficient for basin-scale multisensor optical-radar SWE estimation. 

We investigated the physiographic controls and sensitivities of midwinter snowmelt metrics in the California Sierra Nevada. While future work needs to focus on metrics such as snowmelt rate and melt season length, due to positive biases for melt season dynamics, the SNSR data isn't well suited for this type of analysis. We also recommend that the sensitivity analysis performed here could be upscaled to the WUS using a recently published WUS-wide SWE reanalysis from \cite{fangWesternUnitedStates2022}. Continued efforts to develop high-resolution large-scale, physically based snow models will be crucial in advancing our understanding of the physiographic effects on key snowpack processes.

For continental to global scale implementation of the L-band InSAR SWE retrievals, the two main uncertainties must be addressed: atmospheric correction in complex mountain terrain and methods for confidently identifying the correct reference phase. A near-real-time atmospheric correction method that works across the diverse meteorologic conditions of mountain environments will be exceedingly difficult. Snowpack variations and atmospheric signals scale with elevation, entangling these two signals together. Future snow-focused atmospheric correction work should leverage past methodological advances such as the persistent scatterer (PS) \citep{ferrettiPermanentScatterersSAR2001} and the small baseline subsets (SBAS) approaches \citep{berardinoNewAlgorithmSurface2002,yunjunSmallBaselineInSAR2019}. However, these methods must be designed with near-real-time SWE monitoring in mind and not retrospective geological analysis.

We used L-band InSAR to estimate snowpack variations in an open meadow and lightly forest moderately steep environment. However, this technique will not work in melting conditions, steep topography, and dense canopy cover. A complete understanding of global SWE distributions will require the implementation of various spaceborne radar frequencies, polarizations, and retrieval techniques. SAR retrievals will need to be augmented at the watershed scale by the continued use of airborne lidar surveys. The snow remote sensing community recognizes the utmost importance of a snow-focused satellite mission for SWE retrievals --- currently being proposed at either Ku-band \citep{tsangReviewArticleGlobal2022, garnaudQuantifyingSnowMass2019} or P-band \citep{shahRemoteSensingSnow2017}.  We must also continue to minimize the snow depth uncertainties from C-band retrievals \citep{lievensSnowDepthVariability2019,lievensSentinel1SnowDepth2022} by continuing to investigate the physical mechanisms governing the scattering and implementing higher resolution fSCA and canopy cover information into the algorithm. Understanding the performance of these experimental spatially distributed snow datasets requires spatially distributed validation data; this is best achieved through airborne lidar \citep{painterAirborneSnowObservatory2016} or terrestrial-based lidar data.

No SAR-based SWE retrieval technique will be able to provide spatially complete data. The shorter wavelengths (Ku-band and C-band) are significantly impacted by the forest canopy \citep{rottColdRegionsHydrology2010}. While P-band can penetrate forest canopy, the satellite would provide a few (2--6) narrow swaths ($\sim$1~km) and not spatially complete data \citep{yuehSatelliteSyntheticAperture2021}. Therefore, for spatiotemporally complete data, assimilation of the snow data into land surface models will be required for all SAR-based SWE and snow depth retrievals \citep{girottoDataAssimilationImproves2020}. Assimilation methodologies have been demonstrated at Ku-band \citep{wrzesienDevelopmentNatureRun2022, choEvaluatingUtilityActive2022}, P-band \citep{maEstimatingSpatiotemporallyContinuous2023}, and C-band \citep{girottoIdentifyingSnowfallElevation2023, brangersSentinel1SnowDepth2023}, yet not for L-band. This should be the focus of future studies.

%%
This dissertation builds on the foundation of decades of snow hydrology and remote sensing research. With access to satellite data, high-powered cloud computing, and the robustness of open-source programming tools all quickly advancing, it is an exciting time to be a remote sensing scientist. Continued work to better understand and manage our water resources is vital in an uncertain hydrologic future.


\bibliographystyle{apalike}
\setstretch{1}
\bibliography{ch5.bib}
\setstretch{1.5}
